\chapter{Propagator and joint probability distribution}

\section{General theory for the propagator of two particles}

\subsection{Non-interacting systems}

The propagator for a single particle system is used to find the probability distribution $\tilde{P}(x)$ of a state at anytime, i.e., for a state $\ket{\psi(t_0)}$,
\begin{equation}
    \tilde{P}(q_F, t_F) = \braket{q_F}{\psi(t_F)} = \int K(q_f, q_0; \Dd{t})\psi(q_0, t_0)\dd{q_0}.
\end{equation}
When taken the modulus squared, $|\tilde{P}(q_F, t_F)|^2$, or just $P(q_F, t_F)$, represents the probability of finding that particle at the point $(q_F, t_F)$ in spacetime.

We shall then extend this idea to describe a two particle system. Let there be a state ket $\ket{\eta(t)}$, which simultaneously represents the state of both particle one and particle two. Assume that at some point in time, $\ket{\eta}$ is separable:
\begin{equation}
    \ket{\eta(t_0)} = \ket{\psi(t_0)} \tensor \ket{\phi(t_0)}.
\end{equation}
If the subsystem of $\ket{\eta}$ is non-interacting, the Hamiltonian must be completely separable, which also implies that the time evolution operator $\hat{U}$ is also separable. Consider $\braket{q_F, q_F'}{\eta(t_F)}$ where the unprimed $q$ belongs to the position in the Hilbert space of particle one, and the primed $q$'s, in Hilbert space of particle two.
\begin{align*}
    \braket{q_F, q_F'}{\eta(t_F)} &= \bra{q_F, q_F'}\left(\ket{\psi_i(t_F)}\ket{\phi_i(t_F)}\right) \\
    &= \psi_i(q_F, t_F)\phi_i(q_F', t_F') \\
    &= \iint K_{\psi}(q_F, t_F; q_0, t_0)K_{\phi}(q_F', t_F'; q_0', t_0')\left[\psi_i(q_F, t_F)\phi_i(q_F', t_F')\right] \dd{q_0}\dd{q_0'}.
\end{align*}
For most systems, $K_{\psi}$ and $K_{\phi}$ is identical because both $\psi_i$ and $\phi_i$ is affected by the same potential. But for some, $K_{\psi}$ and $K_{\phi}$ might not be identical. E.g., if $\psi$ is in a potential well, but $\phi$ is a free particle that's infinitely far away. $K_{\psi}$ must be of the potential well, and $K_{\phi}$ must be of the free particle.

It can be seen that $\braket{q_F, q_F'}{\eta(t_F)}$ represents the probability distribution of both the two particles. E.g., for a state ket $\ket{\psi}\tensor\ket{\phi}$,
\begin{align}
    & (\bra*{q_F}\bra*{q_F'})(\ket*{\psi(t_F)}\ket*{\phi(t_F')}) \\
    &= \braket*{q_F}{\psi(t_F)}\braket*{q_F'}{\phi(t_F')} \label{eq:prejointprobability1}\\
    &= \iint\dd{q_0}\dd{q_0'}K(q_F, t_F; q_0, t_0)K(q_F', t_F';q_0', t_0')(\psi(q_0, t_0)\phi(q_0', t_0')) \\
    &= \int\dd{q_0}K(q_F, t_F; q_0, t_0)\psi(q_0, t_0)\int\dd{q_0'}K(q_F', t_F';q_0', t_0')\phi(q_0', t_0'), \label{eq:prejointprobability2}
\end{align}
\cref{eq:prejointprobability1} says that $\braket{q_F, q_F'}{\eta(t_F)}$ is the product of the probability that $\psi$ is at $(q_F, t_F)$, and $(q_F', t_F')$. Therefore, $\braket{q_F, q_F'}{\eta(t_F)}$ represents the joint probability distribution of the two states, and it can be found via the product of propagators,
\begin{equation}
    K(q_F, t_F; q_0, t_0)K(q_F', t_F';q_0', t_0').
\end{equation}

\subsection{Interacting systems}

Let there be a state ket $\ket{\eta}$ which describes the quantum state of two particles. When the two particles are interacting, the time-evolution operator cannot be factored into tensor products of two operators. Therefore, there can only be one combined time-evolution operator for both of the systems:
\begin{equation}
    \hat{U}(t_F, t_0) = \exp[-\im\Dd{t}\left(\frac{\hat{p}^2}{2m} + \frac{\hat{p}'^2}{2m'} + V(\hat{q}, \hat{q}', t)\right)]
\end{equation}
The consequence of the combined time-evolution operator is that, we cannot calculate the joint probability distribution between different time of the subsystem. For simplicity’ sake, let the index $j = i + 1$, where $t_j = t_i + \Dd{t}$ in which $\Dd{t} \appr 0$.
\begin{align}
    &\braket{q_j, q_j'}{\eta(t_j)} \\
    &= \mel{q_j, q_j'}{\hat{U}(t_j, t_i)}{\eta(t_i)}. \\
    &= \iint \dd{q_i}\dd{q_i'} \mel{q_j, q_j'}{\hat{U}(t_j, t_i)}{q_i, q_i'}\braket{q_i, q_i'}{\eta(t_i)}.
\end{align}

As seen, the form of transition element is
\begin{equation}
    \mel{q_j, q_j'}{\exp[-\im\Dd{t}\left(\frac{\hat{p}^2}{2m} + \frac{\hat{p}'^2}{2m'} + V(\hat{q}, \hat{q}', t)\right)]}{q_i, q_i'}.
\end{equation}
The terms in the exponents can be separated due to the vanishing commutator when $\Dd{t} \appr 0$. By separating the terms in the exponents and inserting two complete sets of momentum basis, the equation above turns into
\begin{align}
    & \frac{1}{(2\cpi)^2} \iint\dd{p}\dd{p'} \mel{q_j, q_j'}{\exp[-\im\Dd{t}\frac{\hat{p}^2}{2m}]}{p, p'}\mel{p, p'}{\exp[-\im\Dd{t}\frac{\hat{p}'^2}{2m'}]\exp[-\im\Dd{t}V(\hat{q}, \hat{q}', t)]}{q_i, q_i'} \nonumber\\
    &= \frac{1}{(2\cpi)^2} \iint\dd{p}\dd{p'} \exp[-iu\Dd{t}\left(\frac{p^2}{2m} + \frac{p'^2}{2m'} + V(q_i, q_i, \Dd{t})\right)]\braket{q_j}{p}\braket{q_j'}{p'}\braket{q_i}{p}\conj\braket{q_j'}{p'}\conj \nonumber\\
    &= \frac{1}{(2\cpi)^4} \e^{-\im\Dd{t}V(q_i, q_i', t)} \int\dd{p}\exp[-\im\Dd{t}\frac{p^2}{2m} + \im p(q_j - q_i)]\int\dd{p'}\exp[-\im\Dd{t}\frac{p'^2}{2m'} + \im p'(q_j' - q_i')^2] \nonumber\\
    &= \frac{(mm')^{\frac{1}{2}}}{8\cpi^3\im\Dd{t}}\exp[-\im\Dd{t}V(q_i, q_i', t) + \frac{\im m'}{2\Dd{t}}(q_j' - q_i')^2 + \frac{\im m}{2\Dd{t}}(q_j - q_i)^2].
\end{align}
To find the propagator for an interacting system, we need to perform successive integrals on $q$ and $q'$, i.e.,
\begin{equation}
    K_{\eta} = \idotsint \dd{q_N}\dd{q_N'}\dots\dd{q_1}\dd{q_1'}\mel{q_F, q_F'}{\hat{U}(t_F, t_N)}{q_N, q_N'}\dots\mel{q_1, q_1'}{\hat{U}(t_1, t_0)}{q_0, q_0'}
\end{equation}

Notice that when there is no interaction between the two systems ($V = 0$), the integrals become separable and reduces down to the form of the non-interacting system's propagator but off by a normalization factor.

There are two common forms of interaction, which is the spring interaction and the coulomb interaction. Both of which includes the term $(q_i - q_i')^2$ in $V(q, q')$, which causes major problems in integration. When expanded, there is a $q_iq_i'$ term that makes the integral inseparable which causes the integral pattern to not repeat; therefore, we resort to perturbation.

\subsection{Form of the two particle perturbation series}

The perturbation series for one particle are already given by Feynman in his path integrals textbook:
\begin{equation}
    K_n(F, 0) = \left(-\im\right)^n\idotsint K_0(F, n)\prod_{i = 1}^n V(i)K_0(i, i - 1)\dd{\tau_i}
\end{equation}
where $K_n$ is the $n$'th order perturbation, $K(j, k) = K(q_j, t_j; q_k, t_k)$, $K = \ssum_nK_n$ and $\dd{\tau_i} = \dd{q_i}\dd{q_i}\dd{t_i}$. To apply it with two particles, we extend it:
\begin{equation}
    K_n(F, 0; F', 0') = \left(-\im\right)^n\idotsint K_0(F, n)K_0(F', n')\left[\prod_{i = 1}^nV(i)K_0(i, i - 1)K_0(i', i' - 1)\dd{q_i}\dd{q_i'}\dd{t_i}\right]. \label{eq:generaltwoparticleperturbation}
\end{equation}
We can also expand the joint probability distribution in the form of the perturbation series.
\begin{align}
    \eta(q_F, q_F'; t_F) &= \int K(q_F, q_F'; q_0, q_0'; t_F - t_0)\eta(q_0, q_0'; t_0)\dd{q_0}\dd{q_0'} \\
    &= \int \sum_n K_n(q_F, q_F'; q_0, q_0'; t_F - t_0)\eta(q_0, q_0'; t_0) \dd{q_0}\dd{q_0'} \\
    &= \sum_n \int K_n(q_F, q_F'; q_0, q_0'; t_F - t_0)\eta(q_0, q_0'; t_0) \dd{q_0}\dd{q_0'}
\end{align}

\section{Initial states of choice}
\label{sec:initial_states_of_choice}

We're interested in the time evolution of a Gaussian wave packet, mostly due to its mathematical simplicity. The normalized state of a Gaussian wave packet is given by
\begin{equation}
    \sqrt{\frac{1}{2\cpi\sigma}}\exp[\im p q - \frac{(q - s)^2}{4\sigma^2}]. \label{eq:unentangled_state}
\end{equation}
For two separable particles, its joint probability is
\begin{equation}
    \braket{q, q'}{\eta(t_0)} = \sqrt{\frac{1}{2\cpi\sigma}}\sqrt{\frac{1}{2\cpi\sigma'}}\exp[\im pq - \frac{(q - s)^2}{4\sigma^2}]\exp[\im p'q' - \frac{(q' - s')^2}{4\sigma'^2}]
\end{equation}

As we'll see, the higher order perturbation terms (at least of the spring system) are expressed as the integral of the product between the wave function and some polynomials, which we'll find later.
\begin{align}
    &\braket{q}{\xi(t)} \\ &= \int K_0(q_F, q_0;t_F)\braket{q_0}{\xi(t)}\dd{q_0} \\
    &= \sqrt{\frac{m}{2\cpi\im t_F}}\int\exp[\frac{\im m}{2t_F}(q_F - q_0)^2] \left(\sqrt{\frac{1}{2\cpi\sigma}}\exp[\im p q_0 - \frac{(q_0 - s)^2}{4\sigma^2}]\right)\dd{q_0}. \\
    &= \frac{1}{2\cpi\sqrt{\sigma\sigma'}}\exp[\im pq - \frac{(q - s)^2}{4\sigma^2}]\exp[\im p'q' - \frac{(q' - s')^2}{4\sigma'^2}] \\
    &= \frac{1}{2\cpi}\sqrt{\frac{m}{\im t_F\sigma}}\int\exp[\frac{\im m}{2t_F}(q_F - q_0)^2 + \im p q_0 - \frac{(q_0 - s)^2}{4\sigma^2}]\dd{q_0} \\
    &= \frac{1}{2\cpi}\sqrt{\frac{m}{\im t_F\sigma}}\int\exp[\left(\frac{\im m q_F^2}{2t_F} - \frac{s^2}{4\sigma^2}\right) + q\left(-\frac{\im m q_F}{t_F} + \im p + \frac{s}{2\sigma^2}\right) + q^2\left(\frac{\im m}{2t_F} - \frac{1}{4\sigma^2}\right)]\dd{q_0} \\
    &= \frac{1}{2\cpi}\sqrt{\frac{m}{\im t_F\sigma}} \cdot 2\sigma\sqrt{\frac{\cpi t_F}{-2\im m\sigma^2 + t_F}}\exp[\frac{4 \im m p q_{F} σ^{2} - m q_{F}^{2} + 2 m q_{F} s - m s^{2} - 2 \im p^{2} t_{F} σ^{2} - 2 p s t_{F}}{4 m σ^{2} + 2 \im t_{F}}]  \nonumber\\
    &= \sqrt{\frac{m\sigma}{2m\sigma^2 + \im t_F}}\exp[\frac{4 \im m p q_{F} σ^{2} - m q_{F}^{2} + 2 m q_{F} s - m s^{2} - 2 \im p^{2} t_{F} σ^{2} - 2 p s t_{F}}{4 m σ^{2} + 2 \im t_{F}}].
\end{align}
To plot its probability amplitude, we have to take its modulus squared, which equals to
\begin{equation}
    \frac{m σ}{\sqrt{4 m^{2} σ^{4} + t_{F}^{2}}}\exp[\frac{- 2 m^{2} q_{F}^{2} σ^{2} + 4 m^{2} q_{F} s σ^{2} - 2 m^{2} s^{2} σ^{2} + 4 m p q_{F} t_{F} σ^{2} - 4 m p s t_{F} σ^{2} - 2 p^{2} t_{F}^{2} σ^{2}}{4 m^{2} σ^{4} + t_{F}^{2}}]
\end{equation}

\section{The spring system}

The spring potential is given by $V(q, q') = \frac{k}{2}(q - q')^2$, which I shall let $\alpha = \frac{k}{2}$ for simplicity's sake.

\subsection{First order perturbation term}
\label{sec:spring_1storder}

From \cref{eq:generaltwoparticleperturbation}, set $t_1 = t, t_0 = 0$
\begin{align}
    &K_1(F, 0; F', 0) \nonumber \\
    &= \left(-\im\right)^1\iiint K_0(F, 1)K_0(F', 1')K_0(1, 0)K_0(1, 0')\alpha(q_1 - q_1')^2\dd{q_1}\dd{q_1'}\dd{t}. \\
    &= -\im\alpha\int_0^{t_F}\left[\iint K_0(q_F, q_1; t_F - t)K_0(q_F', q_1'; t_F - t)K_0(q_1, q_0; t)K_0(q_1', q_0'; t)(q_1 - q_1')^2\dd{q_1}\dd{q_1'}\right]\dd{t}. \nonumber
\end{align}
We then let the terms in the square bracket,
\begin{equation}
    \iint K_0(q_F, q_1; t_F - t)K_0(q_F', q_1'; t_F - t)K_0(q_1, q_0; t)K_0(q_1', q_0'; t)(q_1 - q_1')^2\dd{q_1}\dd{q_1'}
\end{equation}
equals $I$; therefore, $K_1 = -\im\alpha\int_0^{t_F} I\dd{t}$.

We then separate $I$ into three integrals:
\begin{gather}
    I_{P1} = \int q_1^2K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t)\dd{q_1} \int K_0(q_F', q_1'; t_F - t)K_0(q_1', q_0'; t)\dd{q_1'}, \label{eq:spring_IP1}\\
    I_{P2} = \int K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t)\dd{q_1} \int q_1'^2K_0(q_F', q_1'; t_F - t)K_0(q_1', q_0'; t)\dd{q_1'}, \label{eq:spring_IP2}\\
    I_{P3} = \int q_1K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t)\dd{q_1} \int q_1'K_0(q_F', q_1'; t_F - t)K_0(q_1', q_0'; t) \dd{q_1'} \label{eq:spring_IP3},
\end{gather}
where $I = I_{P1} + I_{P2} + 2I_{P3}$. The integrals without the factor $q_1$ and $q_1^2$ can be reduced into the kernel for the free particle:
\begin{gather}
    I_{P1} = K_0(q_F', q_0'; t_F)\int q_1^2K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t)\dd{q_1} \\
    I_{P2} = K_0(q_F, q_0; t_F)\int q_1'^2 K_0(q_F', q_1'; t_F - t)K_0(q_1', q_0'; t)\dd{q_1'}
\end{gather}
Since $I_{P2}$ can be obtained by switching all the primed variables with the corresponding unprimed in $I_{P1}$, we're left with two family of integrals:
\begin{equation}
    \int q_1K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t)\dd{q_1} \mathand \int q_1^2K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t)\dd{q_1}. \label{eq:spring_family_of_integrals}
\end{equation}
To evaluate these, we first simplify the product of kernel under the assumption that $t_F > t$.
\begin{align}
    &K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t) \nonumber\\
    &= \sqrt{\frac{m}{2\cpi\im(t_F - t)}}\sqrt{\frac{m}{2\cpi\im t}}\exp[\frac{\im m}{2(t_F - t)}(q_F - q_1)^2 + \frac{\im m}{2t}(q_1 - q_0)^2] \\
    &= \frac{m}{2\cpi}\sqrt{-\frac{1}{t(t_F - t)}} \exp[q_1^2\left(\frac{\im m}{2t} + \frac{\im m}{2(t_F - t)}\right) - q_1\left(\frac{\im m q_0}{t} + \frac{\im m q_F}{t_F - t}\right) + \left(\frac{\im m q_0^2}{2t} + \frac{\im m q_F^2}{2(t_F - t)}\right)] \nonumber \\
    &= \frac{m}{2\cpi}\sqrt{-\frac{1}{t(t_F - t)}} \exp[-q_1^2\left(\frac{m t_F}{2\im t(t_F - t)}\right) - q_1(\im m)\left(\frac{q_0}{t} + \frac{q_F}{t_F - t}\right) - \left(\frac{m}{2\im}\right)\left(\frac{q_0^2}{t} + \frac{q_F^2}{t_F - t}\right)] \nonumber
\end{align}
The normalization factor are pulled out. Both integrals in \cref{eq:spring_family_of_integrals} can be evaluated with
\begin{equation}
    a = \frac{m t_F}{2\im t(t_F - t)}, \quad b = \im m\left(\frac{q_0}{t} + \frac{q_F}{t_F - t}\right) \mathand c = \left(\frac{m}{2\im}\right)\left(\frac{q_0^2}{t} + \frac{q_F^2}{t_F - t}\right)
\end{equation}
in which,
\begin{equation}
    \exp[\frac{b^2}{4a} - c] = \exp[\frac{\im m}{2t_F}(q_F - q_0)^2] = \sqrt{\frac{2\cpi\im t_F}{m}}K_0(q_F, q_0; t_F).
\end{equation}
To summarize,
\begin{align}
    \int q_1K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t)\dd{q_1} &= -\frac{b}{2}\sqrt{\frac{\cpi}{a^3}}\times\frac{m}{2\cpi}\sqrt{-\frac{1}{t(t_F - t)}}\times\sqrt{\frac{2\cpi\im t_F}{m}}K_0(q_F, q_0; t_F) \nonumber\\
    &= -\frac{b}{2}\sqrt{\frac{\cpi}{a^3}} \times \sqrt{\frac{mt_F}{2\cpi\im t(t_F - t)}}K_0(q_F, q_0; t_F), \label{eq:spring_deg1gaussian_form}
\end{align}
and
\begin{equation}
    \int q_1^2K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t)\dd{q_1} = \frac{1}{4}\sqrt{\frac{\cpi}{a^5}}(2a + b^2) \times \sqrt{\frac{mt_F}{2\cpi\im t(t_F - t)}}K_0(q_F, q_0; t_F). \label{eq:spring_deg2gaussian_form}
\end{equation}

On the Gaussian integral with degree one,
\begin{equation}
    -\frac{b}{2}\sqrt{\frac{\cpi}{a^3}} = \sqrt{\frac{2\cpi t}{mt_F^3}}\frac{\sqrt{-\im(t_F - t)^3}}{\im(t_F - t)} \times \left[q_0(t_F - t) + q_Ft\right];
\end{equation}
thus from \cref{eq:spring_deg1gaussian_form},
\begin{align}
    \int q_1K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t) &= \begin{multlined}[t]
        \sqrt{\frac{2\cpi t}{mt_F^3}}\frac{\sqrt{-\im(t_F - t)^3}}{\im(t_F - t)} \times \left[q_0(t_F - t) + q_Ft\right] \\
        \times \sqrt{\frac{mt_F}{2\cpi\im t(t_F - t)}}K_0(q_F, q_0; t_F)
    \end{multlined} \\
    &= -\frac{1}{t_F}\left[q_0(t_F - t) + q_Ft\right]K_0(q_F, q_0; t_F).
\end{align}
On the Gaussian integral with degree two,
\begin{equation}
    \frac{1}{4}\sqrt{\frac{\cpi}{a^5}}(2a + b^2) = -\sqrt{\frac{2\cpi t}{m^3t_F^5}}\frac{\sqrt{\im(t_F - t)^5}}{(t_F - t)^2}\left[m\left(q_0(t_F - t) + q_Ft\right)^2 + \im tt_F(t_F - t)\right];
\end{equation}
and thus,
\begin{align}
    &\int q_1^2K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t)\dd{q_1} \\
    &= \sqrt{\frac{mt_F}{2\cpi\im t(t_F - t)}}K_0(q_F, q_0; t_F)  \times -\sqrt{\frac{2\cpi t}{m^3t_F^5}}\frac{\sqrt{\im(t_F - t)^5}}{(t_F - t)^2}\left[m\left(q_0(t_F - t) + q_Ft\right)^2 + \im tt_F(t_F - t)\right] \nonumber\\
    &= -\frac{1}{mt_F^2}\left[m\left(q_0(t_F - t) + q_Ft\right)^2 + \im tt_F(t_F - t)\right]K_0(q_F, q_0; t_F).
\end{align}

We're now in the place to finally construct the first order propagator term for the spring system. Recall that
\begin{equation}
    K_1 = -\im\alpha\int_0^{t_F} I\dd{t} = -\im\alpha\left[\int_0^{t_F}I_{P1}\dd{t} + \int_0^{t_F}I_{P2}\dd{t} + 2\int_0^{t_F}I_{P3}\dd{t}\right]
\end{equation}
From earlier,
\begin{gather}
    \begin{aligned}
        I_{P1} &= K_0(q_F', q_0'; t_F)\int q_1^2K_0(q_F, q_1; t_F - t)K_0(q_1, q_0; t)\dd{q_1} \\
        &= -\frac{1}{mt_F^2}\left[m\left(q_0(t_F - t) + q_Ft\right)^2 + \im tt_F(t_F - t)\right]K_0(q_F, q_0; t_F)K_0(q_F', q_0'; t_F),
    \end{aligned}
    \\
    \begin{aligned}
        I_{P2} &= K_0(q_F, q_0; t_F)\int q_1'^2 K_0(q_F', q_1'; t_F - t)K_0(q_1', q_0'; t)\dd{q_1'} \\
        &= -\frac{1}{mt_F^2}\left[m\left(q_0'(t_F - t) + q_F't\right)^2 + \im tt_F(t_F - t)\right]K_0(q_F, q_0; t_F)K_0(q_F', q_0'; t_F),
    \end{aligned}
    \\
    \begin{aligned}
        I_{P3} &= -\frac{1}{t_F}\left[q_0(t_F - t) + q_Ft\right]K_0(q_F, q_0; t_F) \times -\frac{1}{t_F}\left[q_0'(t_F - t) + q_F't\right]K_0(q_F', q_0'; t_F) \\
        &= \frac{1}{t_F^2}\left[q_0(t_F - t) + q_Ft\right]\left[q_0'(t_F - t) + q_F't\right]K_0(q_F, q_0; t_F)K_0(q_F', q_0'; t_F).
    \end{aligned}
\end{gather}
Thus,
\begin{multline}
    K_1 = -\im\alpha K_0(q_F, q_0; t_F)K_0(q_F', q_0'; t_F) \frac{1}{t_F^2} \left[-\frac{1}{m}\int_0^{t_F}m\left(q_0(t_F - t) + q_Ft\right)^2 + \im tt_F(t_F - t)\dd{t} \right. \\
    -\frac{1}{m}\int_0^{t_F}m\left(q_0'(t_F - t) + q_F't\right)^2 + \im tt_F(t_F - t)\dd{t} \\
    \left. + \int_0^{t_F}\left[q_0(t_F - t) + q_Ft\right]\left[q_0'(t_F - t) + q_F't\right]\dd{t}\right]
\end{multline}
The integrals are then taken out to be evaluated term by term. Since the integrand of these integrals are all polynomials, we can just plug it into \texttt{SymPy.jl}:
\begin{gather}
    \int_0^{t_F}m\left(q_0(t_F - t) + q_Ft\right)^2 = \frac{t_F^3}{6}\left(2m(q_0 + q_F)^2 + \im t_F\right) \\
    \int_0^{t_F}m\left(q_0'(t_F - t) + q_F't\right)^2 = \frac{t_F^3}{6}\left(2m(q_0' + q_F')^2 + \im t_F\right) \\
    \int_0^{t_F}\left[q_0(t_F - t) + q_Ft\right]\left[q_0'(t_F - t) + q_F't\right]\dd{t} = \frac{t_F^3}{6}\left(2q_0q_0' + q_0q_F' + q_0'q_F + 2q_Fq_F'\right)
\end{gather}
Therefore, the first order perturbation term of the spring system takes the form
\begin{multline}
    K_1(q_F, q_0; q_F', q_0'; t_F) = -\im\frac{\alpha t_F}{6}K_0(q_F, q_0; t_F)K_0(q_F', q_0'; t_F) \\
    \times\left[-2\left(m(q_0 + q_F)^2 + m(q_0' + q_F')^2 + \im t_F\right) + 2q_0q_0' + q_0q_F' + q_0'q_F + 2q_Fq_F'\right]. \label{eq:spring_first_order_perturbation}
\end{multline}

\subsection{Joint probability contribution from the first order perturbation term on a separable state}

As said earlier, we're interested in the time evolution of a Gaussian wave packet earlier, with the initial state of the two particles being
\begin{equation}
    \eta(q_0, q_0; t_0) = \frac{1}{2\cpi\sqrt{\sigma\sigma'}}\exp[\im pq_0 + \im p'q_0' - \frac{(q_0 - s)^2}{4\sigma^2} - \frac{(q_0' - s')^2}{4\sigma'^2}].
\end{equation}
We shall set $t_0 = 0$ for simplicity's sake. The state at any following time $t_F$ is then
\begin{equation}
    \eta(q_F, q_F'; t_F) = \iint\left(K_0(q_F, q_0; q_F', q_0'; t_F - t_0) + K_1(q_F, q_0; q_F', q_0'; t_F - t_0)\right)\eta(q_0, q_0'; t_0)\dd{q}\dd{q_0'}
\end{equation}
Thus, using the first order perturbation term from \cref{eq:spring_first_order_perturbation},
\begin{align}
    \eta(q_F, q_F'; t_F) &= \begin{multlined}[t]
        \frac{1}{2\cpi\sqrt{\sigma\sigma'}}\iint K_0(q_F, q_0; q_F', q_0'; t_F - t_0)\left\{1 - \im\frac{\alpha t_F}{6}\left[-2\left(m(q_0 + q_F)^2 \right.\right.\right.\\
        \left.\left.\left. + m(q_0' + q_F')^2 + \im t_F\right) + 2q_0q_0' + q_0q_F' + q_0'q_F + 2q_Fq_F'\right]\vphantom{\frac{\alpha t_F}{6}}\right\}
        \\ \exp[\im pq_0 + \im p'q_0' - \frac{(q_0 - s)^2}{4\sigma^2} - \frac{(q_0' - s')^2}{4\sigma'^2}]\dd{q_0}\dd{q_0'}
    \end{multlined}
\end{align}
In the end, this integral can be evaluated term by term as Gaussian integrals with the same exponential argument.
\begin{align}
    &\im pq_0 - \frac{(q_0 - s)^2}{4\sigma^2} + \frac{\im m}{2t_F}(q_F - q_0)^2 \\
    &= -\left(\frac{1}{4\sigma^2} - \frac{\im m}{2t_F}\right)q_0^2 - \left(\frac{\im m q_F}{t_F} - \im p - \frac{s}{2\sigma^2}\right)q_0 - \left(\frac{s^2}{4\sigma^2} - \frac{\im m q_F^2}{2t_F}\right),
\end{align}
with
\begin{equation}
    a = \frac{1}{4\sigma^2} - \frac{\im m}{2t_F}, \quad b = \frac{\im m q_F}{t_F} - \im p - \frac{s}{2\sigma^2} \mathand \frac{s^2}{4\sigma^2} - \frac{\im m q_F^2}{2t_F}.
\end{equation}
From \cref{sec:initial_states_of_choice},
\begin{equation}
    \exp[\frac{b^2}{4a} - c] = \exp[\frac{4 \im m p q_{F} σ^{2} - m q_{F}^{2} + 2 m q_{F} s - m s^{2} - 2 \im p^{2} t_{F} σ^{2} - 2 p s t_{F}}{4 m σ^{2} + 2 \im t_{F}}] \equiv \Xi,
\end{equation}
and
\begin{gather}
    \sqrt{\frac{\cpi}{a}} = 2\sigma\sqrt{\frac{\cpi t_F}{t_F - 2\im m\sigma^2}}, \\
    -\frac{b}{2}\sqrt{\frac{\cpi}{a^3}} = 2\sigma\sqrt{\frac{\cpi t_F}{(t_F - 2\im m\sigma^2)^3}}\left(-2\im q_F + 2\im p t_F\sigma^2 + st_F\right), \\
    \frac{1}{4}\sqrt{\frac{\cpi}{a^5}} = 2\sigma\sqrt{\frac{\cpi t_F}{(t_F - 2\im m\sigma^2)^5}}\left(- 4 \im m t_{F} σ^{4} + 2 t_{F}^{2} σ^{2} + \left(- 2 \im m q_{F} σ^{2} + 2 \im p t_{F} σ^{2} + s t_{F}\right)^{2}\right).
\end{gather}

Now let's consider the integral
\begin{align}
    &I_1(p, s, \sigma, m; q_0, n) \\
    &= \int q_0^n K_0(q_F, q_0; t_F)\exp[\im pq_0 - \frac{(q_0 - s)^2}{4\sigma^2}] \dd{q_0} \\
    &= \sqrt{\frac{m}{2\cpi\im t_F}}\int q_0^n\exp[\im pq_0 - \frac{(q_0 - s)^2}{4\sigma^2} + \frac{\im m}{2t_F}(q_F - q_0)^2]\dd{q_0} \\
    &= \sqrt{\frac{m}{2\cpi\im t_F}}\int q_0^n\exp[-\left(\frac{1}{4\sigma^2} - \frac{\im m}{2t_F}\right)q_0^2 - \left(\frac{\im m q_F}{t_F} - \im p - \frac{s}{2\sigma^2}\right)q_0 - \left(\frac{s^2}{4\sigma^2} - \frac{\im m q_F^2}{2t_F}\right)]\dd{q_0} \nonumber
\end{align}
Let's abbreviate $I(q_F, p, s, \sigma, m; q_0, n)$ as $I(n)$ for now. For $n = 0$, $I(0)$ becomes
\begin{align}
    &\int K_0(q_F, q_0; t_F)\exp[\im p q_0 - \frac{(q_0 - s)^2}{4\sigma^2}]\dd{q_0} \\
    &= \sqrt{\frac{m}{2\cpi\im t_F}}\int\exp[-\left(\frac{1}{4\sigma^2} - \frac{\im m}{2t_F}\right)q_0^2 - \left(\frac{\im m q_F}{t_F} - \im p - \frac{s}{2\sigma^2}\right)q_0 - \left(\frac{s^2}{4\sigma^2} - \frac{\im m q_F^2}{2t_F}\right)]\dd{q_0} \\
    &= \sqrt{\frac{m}{2\cpi\im t_F}}\times 2\sigma\sqrt{\frac{\cpi t_F}{t_F - 2\im m\sigma^2}} \times \Xi \\
    &= \sigma\Xi\sqrt{\frac{2m}{\im t_F(t_F - 2\im m \sigma^2)}}.
\end{align}
For $n = 1$,
\begin{align}
    I(1) &= \int q_0 K_0(q_F, q_0; t_F)\exp[\im p q_0 - \frac{(q_0 - s)^2}{4\sigma^2}]\dd{q_0} \\
    &= \sqrt{\frac{m}{2\cpi\im t_F}} \times 2\sigma\sqrt{\frac{\cpi t_F}{(t_F - 2\im m\sigma^2)^3}}\left(-2\im q_F + 2\im p t_F\sigma^2 + st_F\right) \times \Xi \\
    &= \sigma\Xi\sqrt{\frac{2m}{\im t_F(t_F - 2\im m\sigma^2)^3}}\times \left(-2\im q_F + 2\im p t_F\sigma^2 + st_F\right)
\end{align}
For $n = 2$,
\begin{align}
    I(2) &= \int q_0^2 K_0(q_F, q_0; t_F)\exp[\im p q_0 - \frac{(q_0 - s)^2}{4\sigma^2}]\dd{q_0} \\
    &= \sqrt{\frac{m}{2\cpi\im t_F}} \times 2\sigma\sqrt{\frac{\cpi t_F}{(t_F - 2\im m\sigma^2)^5}}\left(- 4 \im m t_{F} σ^{4} + 2 t_{F}^{2} σ^{2} + \left(- 2 \im m q_{F} σ^{2} + 2 \im p t_{F} σ^{2} + s t_{F}\right)^{2}\right) \times \Xi \nonumber\\
    &= \sigma\Xi\sqrt{\frac{2m}{\im t_F(t_F - 2\im m\sigma^2)^5}}\left(- 4 \im m t_{F} σ^{4} + 2 t_{F}^{2} σ^{2} + \left(- 2 \im m q_{F} σ^{2} + 2 \im p t_{F} σ^{2} + s t_{F}\right)^{2}\right)
\end{align}

\subsection{Joint probability contribution from the first order perturbation term on an entangled state}

\subsection{Second order perturbation term}

The second order perturbation term, $K_2$ is
\begin{align}
    K_2 &= \idotsint K_0(F, 2)V(2)K_0(2, 1)V(1)K_0(1, 0)\dd{q_1}\dd{q_1'}\dd{t_1}\dd{q_2}\dd{q_2'}\dd{t_2} \\
    &= \begin{multlined}[t]
        \idotsint K_0(q_F, q_2; t_F - t_2)K_0(q_F', q_2'; t_F - t_2)K_0(q_2, q_1; t_2 - t_1)K_0(q_2, q_1; t_2 - t_1) \\ \times K_0(q_1, q_0; t_1 - t_0)K_0(q_1, q_0; t_1 - t_0)(q_2 - q_2')^2(q_1 - q_1')^2\dd{q_1}\dd{q_1'}\dd{t_1}\dd{q_2}\dd{q_2'}\dd{t_2}
    \end{multlined} \\
    &= \begin{multlined}[t]
        \int_{t_1}^{t_F}\int_{t_0}^{t_F}\left[\idotsint K_0(q_F, q_2; t_F - t_2)K_0(q_F', q_2'; t_F - t_2)K_0(q_2, q_1; t_2 - t_1)\right. \\ \times K_0(q_2, q_1; t_2 - t_1)K_0(q_1, q_0; t_1 - t_0)K_0(q_1, q_0; t_1 - t_0) \left(\vphantom{\left(q_{2}^{\prime}\right)^{2}} q_{1}^{2} q_{2}^{2} - 2 q_{1}^{2} q_{2} q_{2}^{\prime} \right.\\ + q_{1}^{2} \left(q_{2}^{\prime}\right)^{2} - 2 q_{1} q_{2}^{2} q_{1}^{\prime} + 4 q_{1} q_{2} q_{1}^{\prime} q_{2}^{\prime} - 2 q_{1} q_{1}^{\prime} \left(q_{2}^{\prime}\right)^{2} + q_{2}^{2} \left(q_{1}^{\prime}\right)^{2} \\ \left.\left. - 2 q_{2} \left(q_{1}^{\prime}\right)^{2} q_{2}^{\prime} + \left(q_{1}^{\prime}\right)^{2} \left(q_{2}^{\prime}\right)^{2} \right) \dd{q_1}\dd{q_1'}\dd{q_2}\dd{q_2'} \vphantom{\idotsint}\right]\dd{t_1}\dd{t_2}
    \end{multlined}
\end{align}
The integral once again can be broken into nine integrals that must be integrated w.r.t. time twice later on. All those nine integrals have a product of propagator as a multiplier. We shall evaluate those first, separating the primed and unprimed variables.
\begin{align}
    &\begin{multlined}[t]
        K_0(q_F, q_2; t_F - t_2)K_0(q_F', q_2'; t_F - t_2)K_0(q_2, q_1; t_2 - t_1)K_0(q_2, q_1; t_2 - t_1)K_0(q_1, q_0; t_1 - t_0) \\ \times K_0(q_1, q_0; t_1 - t_0)
    \end{multlined} \nonumber \\
    &= \begin{multlined}[t]
        \frac{\im m^3}{8\cpi^3(t_F - t_2)(t_2 - t_1)(t_1 - t_0)}\exp \left[\frac{\im m}{2(t_F - t_2)}\left((q_F - q_2)^2 + (q_F' - q_2')^2\right) \right. \\ \left. + \frac{\im m}{2(t_2 - t_1)}\left((q_2 - q_1)^2 + (q_2' - q_1')^2\right) + \frac{\im m}{2(t_1 - t_0)}\left((q_1 - q_0)^2 + (q_1' - q_0')^2\right)\right]
    \end{multlined}
\end{align}

\section{The delta function collision problem}

The potential for the delta function collision problem is
\begin{equation}
    V = V_0\ddel(q - q')
\end{equation}
where $V_0$ is the strength of the delta function, and is generally considered to be negative.

\subsection{First order perturbation term}

We evaluate the perturbation term similarly to how we did it in \cref{sec:spring_1storder}, starting with the form:
\begin{align}
    &K_1(F, 0; F', 0) \\
    &= -\im\int_0^{t_F}\left[\iint K_0(q_F, q_1; t_F - t)K_0(q_F', q_1'; t_F - t)K_0(q_1, q_0; t)K_0(q_1', q_0'; t)V_0\ddel(q_1 - q_1')\dd{q_1}\dd{q_1'}\right]\dd{t}. \nonumber \\
    &= -\im V_0\int_0^{t_F}\left[\iint K_0(q_F, q_1; t_F - t)K_0(q_F', q_1'; t_F - t)K_0(q_1, q_0; t)K_0(q_1', q_0'; t)\ddel(q_1 - q_1')\dd{q_1}\dd{q_1'}\right]\dd{t} \nonumber
\end{align}
Let $I_1$ represents the integral in the square bracket; thus, $K_1 = -\im V_0\int_{0}^{t_F}I_1\dd{t}$. Then,
\begin{align}
    I_1 &= \iint K_0(q_F, q_1; t_F - t)K_0(q_F', q_1'; t_F - t)K_0(q_1, q_0; t)K_0(q_1', q_0'; t)\ddel(q_1 - q_1')\dd{q_1}\dd{q_1'} \\
    &= \int K_0(q_F, q_1'; t_F - t)K_0(q_F', q_1'; t_F - t)K_0(q_1', q_0; t)K_0(q_1', q_0'; t)\dd{q_1'}
\end{align}

\section{The coulomb problem}